Secure Composition of Robust and Optimising Compilers

### 2023-06-20 popl/main.tex
Introduce filter

\MKin{add filter $\theta$ projecting to specification events}

\begin{theorem}[$\src{L}$-programs are \gls{tms}]\label{thm:wt:tms}
  If $\progstepto{\src{\prog{\library_{\ctx}}{\library_{\comp}}}}{\src{\rtt{\statevar}{\valueexpr}}}{\src{\trace}}$, then $\montmssafe{\filterLtms{\src{\trace}}}$.\Coqed
\end{theorem}

@@

\subsection{$\obj{L_{\scct}}$: A Language with Access to a Model Specific Register}\label{subsec:ltms}

@@

\MKin{compiler $\irl{L_{MS}}\to\obj{L_{\scct}}$}
\MKin{x-lang relations}
\MKin{backtranslation}
\MKin{rtp of scct}

>>>>

\begin{center}
  \judgbox{\thelocmap(\src{\loc})=\loc}{,,Map an $\src{L_{\tmssafe}}$ location to a specification location $\loc$.''}
  \judgbox{\filterLtms{\src{\event}}=\event}{,,Project an $\src{L_{\tmssafe}}$ event $\src{\event}$ to a specification event $\event$.''}
  \typerule{$\src{L_{\tmssafe}}$-filter-context}{
    \src{\event[_b]}\not=\src{\lightning}
  }{
    \filterLtms{\src{\tup{\event[_b]}{\ctx}} = \emptyevent}
  }{ltms-filter-context}
  %
  \typerule{$\src{L_{\tmssafe}}$-filter-abort}{
  }{
    \filterLtms{\src{\lightning}} = \lightning
  }{ltms-filter-abort}
  %
%  \typerule{$\src{L_{\tmssafe}}$-filter-start}{
%  }{
%    \filterLtms{\src{\tup{Start}{\comp}}} = \emptyevent
%  }{ltms-filter-start}
  %
  \typerule{$\src{L_{\tmssafe}}$-filter-alloc}{
    \locmapsto{\src{\loc}}{\loc} &
    \src{n}=n
  }{
    \filterLtms{\src{\tup{Alloc\ \loc\ n}{\comp}}} = \tup{\ev{Alloc}\ \loc\ n}{\comp,\unlock}
  }{ltms-filter-alloc}
\end{center}
To prove that well-typed $\src{L_{\tmssafe}}$ programs are temporal memory safe, a map from $\src{L_{\tmssafe}}$ to specification events (see \Cref{subsec:propdefs}) allows the use of \Cref{def:monsat}.
The map is mostly entirely straight-forward.
Most notably, it filters any action that the context does (\Cref{tr:ltms-filter-context}), since a context is free to do anything.
Of course, a context invoking $\src{\labort}$ to crash the program must not go undetected (\Cref{tr:ltms-filter-abort}).
As for the component, pre--events are essentially recolored to go from blue $\src{L_{\tmssafe}}$ events to the events of the most general trace model (\Cref{tr:ltms-filter-alloc}).
Events that carry locations make use of a location--map from blue $\src{L_{\tmssafe}}$ locations to the more abstract ones.

\MKin{show at least one forward sim lemma or not?}

\begin{lemma}[$\src{L_{\tmssafe}}$-programs are \gls{tms}]\label{lem:wt:tmsmon}
  If $\progstepto{\src{\prog{\library_{\ctx}}{\library_{\comp}}}}{\src{\rtt{\statevar}{\valueexpr}}}{\src{\trace}}$, then $\montmssafe{\filterLtms{\src{\trace}}}$.\Coqed
\end{lemma}
\begin{theorem}[$\src{L_{\tmssafe}}$-programs are \gls{tms}]\label{thm:wt:tms}
  For any $\src{\library_{\comp}}$, $\rsat{\src{\library_{\comp}}}{\tmssafe}$ \Coqed
\end{theorem}

@@

\subsection{$\obj{L_{\scctsafe}}$: A Language with Access to a Model Specific Register}\label{subsec:ltms}

@@

\MKin{compiler $\irl{L_{MS}}\to\obj{L_{\scctsafe}}$}
\MKin{x-lang relations}
\MKin{backtranslation}
\MKin{rtp of scct}
